The importance of a complete description of dependence between variables for ecology and related fields

### 2019-05-03 Paper.Rmd
plot label : cedar creek fixed

\begin{figure}
\begin{center}
\includegraphics[width=6.5in]{./Results/BivarDataPlot.pdf}
\caption{Upper panels show raw data plots for (A) $\log_{10}$(soil C) and $\log_{10}$(soil N) data, (B) $\log_{10}$(basal metabolic rate (BMR)) vs. $\log_{10}$(body mass) 
for birds, (C) the same for mammals, and (D) above-ground plant biomass vs. Shannon's index \textit{(H)} from Cedar Creek. Bottom panels show the corresponding copula plots. See text for units used in upper panels. \label{fig_biv_multi_raw_cop}}
\end{center}
\end{figure}
<!--***DAN: Shya, it say "Avg. H" and "Avg. biomass" on the axes of D. Reading the sup mat
data section carefully, I presume this is because there were multiple strips per plot
and these were averaged. However, the averaging is not mentioned in the main text, so I think
this will be confusing for some readers. Can you please change the axes to read "Biomas" and "H"?-->

>>>>

\begin{figure}
\begin{center}
\includegraphics[width=6.5in]{./Results/BivarDataPlot.pdf}
\caption{Upper panels show raw data plots for (A) $\log_{10}$(soil C) and $\log_{10}$(soil N) data, (B) $\log_{10}$(basal metabolic rate (BMR)) vs. $\log_{10}$(body mass) 
for birds, (C) the same for mammals, and (D) above-ground plant biomass vs. Shannon's index \textit{(H)} from Cedar Creek. Bottom panels show the corresponding copula plots. See text for units used in upper panels. \label{fig_biv_multi_raw_cop}}
\end{center}
\end{figure}
